---
title: "MultiHead Simulation"
author: "Danilo Cillario"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Packaging Simulation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

With `simulateMH()` is possible to simulate the results of the Multi Head Weighting Machine that produce a box of praline.
These machine weights the input praline and try to produce multi box of its where the box weight exceeds the declared weight of the minimun quantity possible.

## Function

Below the sintax of the function `simulateMH()`:

    res <- simulatePack(source, target, declared, min.pcs, step=1000)
    
where:

    source	    :   a vector containing the weight of the single praline
    target      :   the target weight of the MultiHead
    declared    :   declared weight (not used)
    min.pcs     :   the minimun number of piece in the box (only to check the results)
    step        :   simulation steps, number of pack to be simulated

    res         :   result list, containing:
                    res[['data']]    data frame of all single pack simulated
                    res[['result']]  data frame of the rusults

### Algorithm

.....


## Examples

In the following example we could see the frequency distribution of the weight of a box containing 15 Ferrero Raffaello 
using 100 weight of single praline generated with `rnorm()` 

```{r echo=TRUE, fig.heigth=6, fig.show='hold', fig.width=7.1, message=FALSE, warning=FALSE, results='hold'}
library(ggplot2)
library(tecTools)
dati <- rnorm(100, 10.1, 0.3)
b <- simulateMH(dati, 150, 150, 15)
```

is possible check the simulation results:

```{r, echo=1, eval=2,  fig.show='hold', fig.width=7.1, fig.heigth=6, warning=FALSE, results='hold'}
head(b[['data']], 5)
knitr::kable(head(b[['data']], 5))
```

or to plot the weight of the simulated boxes:

```{r, echo=TRUE, fig.show='hold', fig.width=7.1, fig.heigth=6, warning=FALSE, results='hold'}
hist(b[['data']]$peso, xlab='g', main='Peso delle confezioni')
```

or to check the number of pieces in the simulated boxes:

```{r, echo=TRUE, fig.show='hold', fig.width=7.1, fig.heigth=6, warning=FALSE, results='hold'}
b[['results']]
```

or manually:

```{r, echo=TRUE, fig.show='hold', fig.width=7.1, fig.heigth=6, warning=FALSE, results='hold'}
paste(length(b[['data']]$pezzi[b[['data']]$pezzi == 15]), ' box contains ', 15, ' pieces', sep='')
paste(length(b[['data']]$pezzi[b[['data']]$pezzi == 16]), ' box contains ', 16, ' pieces', sep='')
paste(length(b[['data']]$pezzi[b[['data']]$pezzi == 17]), ' box contains ', 17, ' pieces', sep='')
```


## Reference

None

