---
title: "Packaging Simulation"
author: "Danilo Cillario"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Packaging Simulation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

With `simulatePack()` is possible to:

* simulate the weight distribution of a mixed box of product
* check the declared weight of the box 
* check if it possible to change the declared weight of the box

## Function

Below the sintax of the function `simulatePack()`:

    simulatePack(source, composition, declared, plotce = F, main = "Pesi medi", step = 1e+05)
    
where:

    source	    :   a data frame with the weight of the single praline
    composition :   a data frame with the composition of the pack
    declared    :   declared weight
    plotce      :   boolean, T if you want to plot T1 and T2, otherwise F
    main        :   optional main title
    step        :   simulation steps, number of pack to be simulated


### Data Frame structure

```{r, echo=FALSE}
library(ggplot2)
library(tecTools)
```

In the `source` data frame we save the weight of a sample af all the product we want to use in a mixed box:

```{r, echo=TRUE}
data(source)                     # load Thorntons Continental Praline weight
knitr::kable(head(source, 5))
```

In the `composition` data frame we save the composition of the mixed box:

```{r, echo=TRUE}
data(composition)                # composition of Thorntons Continental box
knitr::kable(composition)
```


## Examples

In the following example we could see the frequency distribution of the weight of a box containing 16 Ferrero Rocher 
using the weight of the single praline products on line 1 of Alba

```{r, echo=TRUE, fig.show='hold', fig.width=7.1, fig.heigth=6, warning=FALSE, results='hold'}
library(ggplot2)
library(tecTools)
data(L1_max)                   # load Rocher weight
a <- data.frame(RO=c(16))      # composition of box of T.16 Rocher
simulatePack(L1_max, a, 200.5)
```

the same plotting the T1 and T2 according to Dir. n. 76/211/CEE

```{r, echo=TRUE, fig.show='hold', fig.width=7.1, fig.heigth=6, warning=FALSE, results='hold'}
library(ggplot2)
library(tecTools)
data(L1_max)                   # load Rocher weight
a <- data.frame(RO=c(16))      # composition of box of T.16 Rocher
simulatePack(L1_max, a, 200.5, plotce=T)
```

## Reference

The calculation of T1 and T2 are based on Dir. n. 76/211/CEE (Legge 25.10.78 n.690 in Italy) "approximation of the laws of the Member States relating to the making-up by weight or by volume of certain prepackaged products " ^[available in internet]:

> http://eur-lex.europa.eu/legal-content/it/ALL/?uri=CELEX%3A31976L0211
